Graphical formalization and automated computing of safety constraints in robotics

### 2012-09-17 paper/Paper.tex
Formatting stuff

Furthermore we want to integrate some mechanism to support users in finding suitable constraints for a certain application. We assume that applications are modeled by state transition graphs. This modeling paradigm is used in many healthcare robots that employ dialogue systems for communicating with users~\cite{Bickmore2006}. Other possible fields might be shop assistant robots or entertainment robots. For such kinds of robots, our approach is suitable. It is based on heuristically analyzing state transition graphs and deriving constraints related to the graph structure. In this work, we want to investigate a particular heuristic as a first step towards user support.

Furthermore, we will present some results of applying this heuristics to the medication reminder example described before. The minimum goal that should be achieved was the identification of the following constraints:

@@

\begin{itemize}
	\item Each operator has a different significant visual appearance; in this case we have used color. This kind of classification enables a faster subconscious identification by the user.
	\item The layout of constraints (nested operators) has two dimensions with a certain meaning. Figure~\ref{fig:directions} demonstrates the ``logical'' vertical read direction as well as the time releveant horizontal line.
	\item Multiple nested operators of the same kind which have no order priorities such as \emph{OR} or \emph{AND} appear unnecessarily complex. These operators can be merged.
\end{itemize}

@@

Some improvements on the feature side of the language or the editor were already identified. For example, the state proposition (currently the only supported proposition type) used in constraint formulation might be not enough for other domains. Supporting propositions based on strings or mumerical equations might be necessary. Finally, the only result of constraint checking presented to the user currently is whether the constraint is valid or invalid. In contrast to conventional model checking no additional explanation for the outcome such as a counter example is given. It can be considered to extend the visual language with support for bug identification by a visualization of counter examples, for example.
%\item Substitution of parts of constraints would be nice in order to make it easier to understand. (A simple operator which abstracts from a more complex operator). It's comparable to composite states of hirachical state machines.

>>>>

Furthermore we want to integrate some mechanism to support users in finding suitable constraints for a certain application. We assume that applications are modeled by state transition graphs. This modeling paradigm is used in many healthcare robots that employ dialogue systems for communicating with users~\cite{Bickmore2006}. Other possible fields might be shop assistant robots or entertainment robots. For such systems, our approach is suitable. It is based on heuristically analyzing state transition graphs and deriving constraints related to the graph structure. In this work, we want to investigate a particular heuristic as a first step towards user support.

Finally, we will present some results of applying this heuristics to the medication reminder example described before. The minimum goal that should be achieved was the identification of the following constraints:

@@

\begin{itemize}
	\item Each operator has a different significant visual appearance; in this case we have used color. This kind of classification enables a faster subconscious identification.
	\item The layout of constraints (nested operators) has two dimensions with a certain meaning. Figure~\ref{fig:directions} demonstrates the ``logical'' vertical read direction as well as the time releveant horizontal line.
	\item Multiple nested operators of the same kind which have no order priorities such as \emph{OR} or \emph{AND} appear unnecessarily complex. These operators can be merged.
\end{itemize}

@@

Some improvements on the feature side of the language or the editor were already identified. For example, the state proposition (currently the only supported proposition type) used in constraint formulation might be not enough for other domains. Supporting propositions based on strings or mumerical equations might be necessary. Finally, the only result of constraint checking presented to the user currently is whether the constraint is valid or invalid. \newpage In contrast to conventional model checking no additional explanation for the outcome such as a counter example is given. It can be considered to extend the visual language with support for bug identification by a visualization of counter examples, for example.
%\item Substitution of parts of constraints would be nice in order to make it easier to understand. (A simple operator which abstracts from a more complex operator). It's comparable to composite states of hirachical state machines.
